Methods for Projecting Population Growth

### 2018-04-30 final/tex/Paper.tex
More shit not working :(

In order to understand just a how a few of these models operate, this paper will explore 2 separate models: standard logistic growth and a modified Lotka-Volterra model.

>>>>

In order to understand just a how a few of these models operate, this paper will explore 3 separate models: standard logistic growth (LG), logistic growth augmented with migration data (LGM), and a modified Lotka-Volterra model (MLV). Each model has its own strengths and weaknesses and perform differently in comparison to actual data provided by the United Nations World Bank.

\section{Logistic Growth}

The Logistic Growth model is colloquially defined as:

\begin{align*}
	P(t) = \frac{K N_0 e^{\gamma t}}{K + N_0 (e^{\gamma t} - 1)}
\end{align*}
with $K$ being the theoretical maximum sustainable population, $N_0$ the initial population at time $t_0$, $\gamma$ being the yearly growth rate, and $t$ being the time since $t_0$.

While $N_0$ is trivially obtained from the dataset, $\gamma$ and $K$ are not so simple to obtain. These values are optimized utilizing the least squares method on the dataset, which contains census data since 1910. This produces a model that very closely matches the data, as seen in Figure 1.

\begin{figure}[ht!]
\centering
\includegraphics[width=90mm]{images/lr-graph.png}
\caption{Results of using least squares on logistic growth \label{overflow}}
\end{figure}
